Summary Tables

### 2022-10-11 summary_tables.Rmd
initial outputs for Africa/India

# Export ylls HB
write.csv(rbindlist(health$ylls$hb, use.names = T),
            "results/multi_city/health_impacts/ylls_hb_lng.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(rbindlist(health$ylls$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/ylls_pathway_hb_lng.csv",
            row.names = F)
# Export deaths HB
write.csv(rbindlist(health$deaths$hb, use.names = T),
            "results/multi_city/health_impacts/deaths_hb_lng.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(rbindlist(health$deaths$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/deaths_pathway_hb_lng.csv",
            row.names = F)
```

>>>>

# Export ylls HB
write.csv(rbindlist(health$ylls$hb, use.names = T),
            "results/multi_city/health_impacts/ylls_hb_lng.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(rbindlist(health$ylls$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/ylls_pathway_hb_lng.csv",
            row.names = F)
# Export deaths HB
write.csv(rbindlist(health$deaths$hb, use.names = T),
            "results/multi_city/health_impacts/deaths_hb_lng.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(rbindlist(health$deaths$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/deaths_pathway_hb_lng.csv",
            row.names = F)
